---
title: "Tenary Plot"
author: "Mirco Brunner"
text & data: "Baxter & Cool 2016. http://www.barbicanra.co.uk/simple-r.html"
bibliography: library.bib
output: html_document
keep_md: true
editor_options: 
chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri(file.path(R.home("doc"), "html", "logo.jpg")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;')
```

## Introduction

All data and some Text are from [@baxter_basic_2016] <http://www.barbicanra.co.uk/simple-r.html>.

Histograms are one of the most familiar methods for presenting continuous data.
For illustration unpublished data from Cool (1983) will be used. They are the
lengths (mm) of 90 copper alloy hairpins from southern Britain, 55 classified as
early and 35 as late on archaeological grounds (see Cool, 1990, for a review of the
use of such hairpins). The data are given in Table 4.1.

```{r}
#load libraries
library(ggplot2)
```


## show data table
```{r}
#show data
pins <- read.csv("data_pins/pins.csv")
print(pins)
```

## Figure 4.3a – Based on Table 4.2 (pins)

```{r}
Length <- pins$Length
hist(Length)
```



